Test-driven Knowledge Graph Construction

### 2023-05-08 doc/paper4.tex
Editing

\section{Motivation}
Following a method for knowledge graph construction offers several benefits. In general, a~method helps decide what to do next. In particular, it helps to overcome the blank canvas paralysis at the beginning. Moreover, a method breaks down the effort required for knowledge graph construction into sub-tasks, which can help organize and coordinate a team working on them.

The direction provided by a method anchored in user requirements can reduce the undirected upfront effort and help avoid over-engineering. For example, it discourages needless effort spent on achieving a lossless transformation to the target knowledge graph that preserves all source data even though it might not be needed. It can help avoid premature abstraction and premature optimization, such as for performance or readability. Thanks to the tests checking if the user requirements are satisfied, we get an early proof of value instead of speculating about it. Additionally, the explicit links between requirements and tests allow to assess the requirements traceability and coverage.

@@

A fundamental feature of this cycle is that it intertwines development with testing, so that tests exercise the development artifacts and provide feedback informing further work. Tests provide a controlled way to evolve the artifacts under development in response to changing requirements, such as when their scope is extended or they are refined iteratively. The field of ontology engineering is already adopting agile development approaches using tests. Ontology-specific methods, such as SAMOD \cite{Peroni2016} or Linked Open Terms \cite{PovedaVillalon2022}, are being proposed.

@@

    \item Analyze the CQs to extract terms and relations. CQs can be analyzed using the linguistic notion of presupposition, which can be defined as \textit{"a condition that must be met for a~linguistic expression to have a denotation"} \cite{Ren2014}. Viewed this way, CQs presuppose the terms with which they can be expressed. The terms to extract from CQs are typically nouns or noun phrases that refer to entities from the domain of the knowledge graph under construction. They can be considered lexical surface forms of these entities. The~terms can be identified manually or with the help of tools, such as part-of-speech tagging. The~relations to extract might be represented by verbs connecting the terms co-occurring in a CQ. Less direct mappings between entities and surface forms are possible too.
    \item Formalize the terms and relations in a minimum viable ontology using RDF Schema \cite{Brickley2014}. While terms typically map to classes (i.e. instances of \texttt{rdfs:Class}), relations map either to properties (i.e. instances of \texttt{rdf:Property}) or n-ary relations represented by classes. Document the ontology with definitions sourced from and validated by subject-matter experts to create a shared understanding. The ontology should make minimal ontological commitment, so limit its upfront axiomatization, such as OWL restrictions. The resulting ontology shall serve as an explicit and machine-readable conceptualization of the knowledge graph's domain. Formalizing the ontology may in turn reveal ambiguity in the CQs. Ambiguous CQs cannot be formalized reliably since misinterpretations may occur. In such cases, sources of ambiguity should be revised with subject-matter experts aiming to reformulate the CQs in an unambiguous way.
    \item Translate the CQs to SPARQL queries expressed by the ontology. SPARQL queries make the CQs executable. Here, we expect a manual translation of the CQs to SPARQL queries. Automated translation was attempted by others, such as in \cite{EspinozaArias2022}. Start with syntactically valid SPARQL queries of hypothetical data expressed by the ontology. A CQ may translate to a SPARQL graph pattern composed of triple patterns joining the terms co-occurring in the question via specific relations. The way CQs should be translated to SPARQL queries largely depends on their expected answers. Ren et al. \cite{Ren2014} suggests that we might be \textit{"more interested in checking if a CQ can be meaningfully answered, instead of directly answering a~CQ."} When using such existential quantification, a SPARQL query formalizing a CQ can be expected to return non-empty results. What it means is that the query can answer a~CQ using a~given knowledge graph. It does not verify if the answer is correct. Conversely, some CQs may describe universal invariants of their domain. Queries encoding these invariants are akin to property-based testing \cite{Fink1997}. In case stricter guarantees are needed, the expected correct answers can be included in the queries and validation constraints in SHACL implementing the CQs, corresponding to the usual example-based testing.
    \item Wrap the queries as SPARQL-based SHACL constraints to automate their execution. SHACL defines a target\footnote{\urlshacltargets} of each constraint. A target defines the scope of a CQ. Scope of the data graph validated by a given constraint may either encompass the entire knowledge graph or cover its subset. For instance, existentially quantified queries checking the complete data graph can target it by using \texttt{sh:targetNode}. It is also possible to rewrite a part of a SPARQL query translating a CQ as target selection in SHACL. Alternatively, the prerequisite part of the query can be represented as a SPARQL-based target \cite{SHACLAF2017}. An~entity-centric partitioning can be implemented by defining a SPARQL-based target that covers a concise bounded description \cite{Stickler2005}. Some data sources for the knowledge graph may natively partition data to independent subsets, such as API responses or messages from a queue, that can be effectively validated by specific subsets of SHACL constraints. SHACL also defines the criteria of correctness of the SPARQL queries. An \texttt{sh:ask} query is expected to return the boolean \texttt{true}, while any results produced by an sh:select query are treated as violations. Specific expected results can be either hard-coded into the queries or specified via \texttt{sh:hasValue} in case a single value is expected. When including the expected results in SPARQL-based constraints, we may run into the limitations of SHACL due to pre-binding of variables.\footnote{\urlshaclprebinding} For example, the \texttt{VALUES} clause, which could represent results of \texttt{SELECT} queries, is not allowed.

>>>>

\section{Motivation}
Following a method for knowledge graph construction offers several benefits. In general, a~method helps decide what to do next. In particular, it helps to overcome the blank canvas paralysis at the beginning and jump-start the work. Moreover, a method breaks down the effort required for knowledge graph construction into sub-tasks, which can help organize and coordinate a team working on them.

The direction provided by a method anchored in user requirements can reduce the unfocused upfront effort and help avoid over-engineering. For example, it discourages needless effort spent on achieving a lossless transformation that preserves all source data in the produced knowledge graph even though it might not be needed. It can help avoid premature abstraction and premature optimization, such as for performance or readability. Thanks to the tests checking if the user requirements are satisfied, we get an early proof of value instead of speculating about it. Additionally, the explicit links between requirements and tests allow to assess the requirements traceability and coverage.

@@

A fundamental feature of this cycle is that it intertwines development with testing, so that tests exercise the developed artifacts and provide feedback informing further work. Tests provide a controlled way to evolve the artifacts under construction in response to changing requirements, such as when their scope is extended or when they are refined iteratively. The field of ontology engineering is already adopting agile development approaches using tests. Ontology-specific methods, such as SAMOD \cite{Peroni2016} or Linked Open Terms \cite{PovedaVillalon2022}, are being proposed.

@@

    \item Analyze the CQs to extract terms and relations. CQs can be analyzed using the linguistic notion of presupposition, which can be defined as \textit{"a condition that must be met for a~linguistic expression to have a denotation"} \cite{Ren2014}. Viewed this way, CQs presuppose the terms with which they can be expressed. The terms to extract from CQs are typically nouns or noun phrases that refer to entities from the domain of the knowledge graph under construction. They can be considered lexical surface forms of these entities. The~terms can be identified manually or with the help of tools, such as part-of-speech tagging. The~relations to extract might be represented by verbs connecting the terms co-occurring in a CQ. Less direct mappings between entities and surface forms are possible too, such as when a surface form provides the context disambiguating an entity.
    \item Formalize the terms and relations in a minimum viable ontology using RDF Schema \cite{Brickley2014}. While terms typically map to classes (i.e. instances of \texttt{rdfs:Class}), relations map either to properties (i.e. instances of \texttt{rdf:Property}) or n-ary relations represented by classes. Document the ontology with definitions sourced from and validated by subject-matter experts to create a shared understanding. The ontology should make minimal ontological commitment to aid its evolution, so limit its upfront axiomatization, such as by using OWL restrictions. The resulting ontology shall serve as an explicit and machine-readable conceptualization of the knowledge graph's domain. Formalizing the ontology may in turn reveal ambiguity in the CQs. Ambiguous CQs cannot be formalized reliably since their misinterpretations may occur. In such cases, the sources of ambiguity should be revised with subject-matter experts while aiming to reformulate the CQs in an unambiguous way.
    \item Translate the CQs to SPARQL queries expressed by the ontology. SPARQL queries make the CQs executable. Here, we expect a manual translation of the CQs to SPARQL queries. Automated translation was attempted by others, such as in \cite{EspinozaArias2022}. Start with syntactically valid SPARQL queries of hypothetical data expressed by the ontology. A CQ may translate to a SPARQL graph pattern composed of triple patterns joining the terms co-occurring in the question via specific relations. The way CQs should be translated to SPARQL queries largely depends on their expected answers. Ren et al. \cite{Ren2014} suggest that we might be \textit{"more interested in checking if a CQ can be meaningfully answered, instead of directly answering a~CQ."} When using such existential quantification of the desired answers, a SPARQL query formalizing a CQ can be expected to return non-empty results. What it means is that the query can answer a~CQ using a~given knowledge graph. It does not verify if the answer is correct. Conversely, some CQs may describe universal invariants of their domain. Queries encoding these invariants are akin to property-based testing \cite{Fink1997}. In case stricter guarantees are needed, the expected correct answers can be included in the queries and validation constraints in SHACL implementing the CQs, corresponding to the usual example-based testing.
    \item Wrap the queries as SPARQL-based SHACL constraints to automate their execution. SHACL defines a target\footnote{\urlshacltargets} of each constraint. In our context, a target sets the scope of a CQ. The scope of the data graph validated by a given constraint may either encompass the entire knowledge graph or cover its subset. For instance, existentially quantified queries checking the complete data graph can target it by using \texttt{sh:targetNode}. It is also possible to rewrite a part of a SPARQL query translating a CQ as target selection in SHACL. Alternatively, the prerequisite part of the query can be represented as a SPARQL-based target \cite{SHACLAF2017}. An~entity-centric partitioning can be implemented by defining a SPARQL-based target that covers a concise bounded description \cite{Stickler2005}. Some data sources for the knowledge graph may natively partition data to independent subsets, such as API responses or messages from a queue, that can be effectively validated by specific subsets of SHACL constraints. SHACL also defines the criteria of correctness of the SPARQL queries. An \texttt{sh:ask} query is expected to return the boolean \texttt{true}, while any results produced by an sh:select query are treated as violations. Specific expected results can be either hard-coded into the queries or specified via \texttt{sh:hasValue} in case a single value is expected. When including the expected results in SPARQL-based constraints, we may run into the limitations of SHACL due to pre-binding of variables.\footnote{\urlshaclprebinding} For example, the \texttt{VALUES} clause, which could represent results of \texttt{SELECT} queries, is not allowed.
